---
title: "FROC_task_and_resulting_FROC_data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{FROC_task_and_resulting_FROC_data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Definition of FROC task

We explain how the following FROC data arise from FROC task in this vignette.

Format of dataset for FROC analysis:
 
 
 Confidence Level    | No. of Hits | No. of False alarms
 :-----|----------|-------------
5 = definitely present |  $H_{5}$ |  $F_{5}$ 
4 = probably present   |  $H_{4}$ |  $F_{4}$ 
3 = equivocal          |  $H_{3}$ |  $F_{3}$ 
2 = probably absent    |  $H_{2}$ |  $F_{2}$ 
1 = questionable       |  $H_{1}$ |  $F_{1}$ 


Assume that there is 

 - Images (radiographers) contains  diseased cases and healthy cases.
 - readers who try to find lesions from images
 - gold standard, specify which is lesion. So each image given which shadow is lesion or not.
 

In FROC task, reader response the locations of suspicious shadows in image with his confidence level. If reader answer over all images, then by the gold standard, each readers answers are associated hit or false alarms whether or not reader correctly answer his locations on true lesions or not.

So, this manner, we get the FROC data.
If image has some indicator function representing the category of imaging methods, then such case, data will be the multiple reader and multiple modality.

# Single reader and single modality from R console

```{r}
library(BayesianFROC)

BayesianFROC::viewdata(d)
```

# Multiple reader and multiple modality from R console

```{r}
library(BayesianFROC)

BayesianFROC::viewdata(dd)
```


# For more correct English ...

see my paper in which proof reading had done and thus I think it is more easy to read. Good Luck !!

# I quit my company for my health being bad.

I have deseased  many prurigo, it very ... 

I have to work, If there is job, please tell me.

# Rjafroc 

In my package is independent to Rjafroc, but relates it. But now 2019 May, the Rjafroc is not on CRAN, so I cannot link to Rjafroc.

In my program completely independent to Rjafroc, so it is no problem wheter Rjafroc is on CRAN or not.
