---
title: "Very Very Brief Description"
output: rmarkdown::html_vignette
author: "Issei Tsunoda"
date: "`r Sys.Date()`"
vignette: >
  %\VignetteIndexEntry{Very_Very_Brief_Description}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


<style type="text/css">

h1.title {
  font-size: 35px;
  font-weight: bold;
  font-family: Arial-Black;
   color: #800000			;
}
h1{
  font-size: 35px;
  font-weight: bold;
  font-family: Arial-Black;
  
  color: #800000			;

}

h2 {
  font-size: 30px;
  font-weight: bold;
  font-family: Arial-Black;
    
  color: #800000			;

}

h3 {
  font-size: 26px;
  font-weight: bold;
  font-family: Arial-Black;
    
  color: #800000			;

}

h4 {
  font-size: 24px;
  font-weight: bold;
  font-family: Arial-Black;
    
  color: #800000			;

}



h5 {
  font-size: 22px;
  font-weight: bold;
  font-family: Arial-Black;
    
  color: #800000			;

}



h6 {
  font-size: 19px;
  font-weight: bold;
  font-family: Arial-Black;
    
  color: #800000			;

}



img {
	border:0;
}


body {
  font-size: 18px;
  <!-- font-weight: normal ; -->
    font-weight:bolder;
  
  font-family: Calibri;
  
    
  color: #800000			;

  background-color:#EEEEEE;	
  
<!--   margin:0; -->
<!-- 	padding:0; -->
  
}












p {
    color: #440000		;
}

</style>


 Nowadays many people  spent very hard days night, working like a dog, so, it is for such  doggy.

I love doggy, I want to meet doggy. I do not want to work like a doggy,... I forget that I do not have any job. Please employ me or I have to...




##### Graphical User Interface: GUI
```{r,eval=FALSE}
library(BayesianFROC)
          BayesianFROC::fit_GUI() #   Enjoy fitting!

```

 
Or


```{r,eval=FALSE}
library(BayesianFROC)
          fit_GUI_dashboard() #   Enjoy fitting!

```

 
           

Or


```{r,eval=FALSE}
library(BayesianFROC)
           fit_GUI_simple() #   Enjoy fitting!

```

 



#  $\color{green}{\textit{Single reader and Single modality }}$

## Data 



 Confidence Level    | No. of Hits | No. of False alarms
 :-----|----------|-------------
5 = definitely present |  $H_{5}$ |  $F_{5}$ 
4 = probably present   |  $H_{4}$ |  $F_{4}$ 
3 = equivocal          |  $H_{3}$ |  $F_{3}$ 
2 = probably           |  $H_{2}$ |  $F_{2}$ 
1 = questionable       |  $H_{1}$ |  $F_{1}$ 

where, $H_{c},F_c \in \mathbb{N} \cup\{0\}$ for $c=1,2,...,5$.

 - $N_I$: Number of images
 - $N_L$: Number of lesions


## Model 









$$
H_c \sim \text{Binomial}(p_c(\theta),N_L),\\
F_c \sim \text{Poisson}(q_c(\theta)).\\
$$


$$
p_c(\theta) := \int_{\theta_c}^{\theta_{c+1}}\text{Gaussian}_{}(x|\mu,\sigma)dx,\\
q_c(\theta) := \int_{\theta_c}^{\theta_{c+1}}N_I \times \frac{d \log \Phi(z)}{dz}dz.
$$



where model parameter  is   $\theta = (\theta_1,\theta_2,\theta_3,...\theta_C; m,v)$ which should be estimated and $\Phi$ denotes the cumulative distribution functions of canonical Gaussian.








## R script 
 
```{r , eval=FALSE}
d   <- BayesianFROC::d
fit <- fit_Bayesian_FROC(  dataList = d )
```






## Criticism to classical FROC theory

One notice that our model is use two distribution for hit and false alarm rate, one is the latent Gaussian and the another is a differential logarithmic Gaussian, which differ the so-called bi normal assumption. More precisely, we do not use the canonical Gaussian for the noise distribution, but we use the differential logarithmic Gaussian instead. 


## Difficulty

My Bayesian models is quite new, and I did not refer any paper except Charaborty 1989 paper. Thus manu people cannot understand where is it difficult to make model. I first make this model with full heterogeniety, but it did not converge, thus I reduce parameters so that MCMC converge.  

Making a model is very very simple and easy, but when we try to run MCMC it will fail for many models. We have to construct models so that MCMC converges. 
























